### 2011-11-04 doc/pldi2012/highlevel.tex
More text for the high level runtime section

\subsection{Execution}

\subsection{Task Completion}

>>>>

\subsection{Execution}
\label{subsec:execution}
Once task mapping is complete the high level runtime performs the necessary operations
to be issue the task to the low level runtime.  It first creates any new physical instances
for the regions which the task requires.  It then issues the necessary copies required
for the task to execute contignent on the tasks producing the source physical instances
have finished.  Then it issues the task itself to the low level processor contingent
on all the copies for the task haveing finished as well as the the set of tasks
on which the issuing task dependends having finished.  These dependences are all encoded
using event dependencies in the low level runtime.  Once all the necessary events
have triggered the task will be run.

Once a task starts running, the runtime is asked to create the region accessors for
the task.  The runtime investigates whether or not fast accessors can be created for
each of the regions that the task requires.  Fast accessors are described in more
detail in section \ref{sec:fastaccess}.  If fast accessors can be created for every
region in a task, then the runtime chooses to execute a task instantiated with fast
region accessor methods.  However, if any region can not be specialized into a fast
accessor the runtime defaults to a task instantiation that relies on {\tt get} and
{\tt put} operations to access regions.

The runtime will also return to the executing task a unique identifier describing the
context in which the task is executing.  All calls into the runtime require the task
to pass this context identifier which is what permits the runtime to know the context
for incoming calls.

\subsection{Task Completion}
\label{subsec:cleanup}
